### 2014-04-14 patchy-selection-paper.tex
.

% \newcommand{\var}{\mathop{\mbox{Var}}}
% \newcommand{\Exp}{\mathop{\mbox{Exp}}}
\DeclareMathOperator{\var}{Var}
\DeclareMathOperator{\Exp}{Exp}
\DeclareMathOperator{\sn}{sn}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\calE}{\mathcal{E}}
\newcommand{\calC}{\mathcal{C}}
\newcommand{\dconv}{\xrightarrow{d}}
\newcommand{\deq}{\stackrel{\scriptscriptstyle{d}}{=}}

@@

>>>>

% \newcommand{\var}{\mathop{\mbox{Var}}}
% \newcommand{\Exp}{\mathop{\mbox{Exp}}}
\DeclareMathOperator{\var}{Var}
\DeclareMathOperator{\Exp}{Exp}
\DeclareMathOperator{\sn}{sn}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\calE}{\mathcal{E}}
\newcommand{\calC}{\mathcal{C}}
\newcommand{\dconv}{\xrightarrow{d}}
\newcommand{\deq}{\stackrel{\scriptscriptstyle{d}}{=}}

@@

\subsection{Temporary}

Consider a single migrant family $Z$ beginning at $x$.
Let $B_t$ be a Brownian motion with variance $\sigma^2$, 
and $\tau_\dagger$ an independent Exponential($\alpha$) time.
The mean occupation time of $Z$ spent in a region $A$ is 
\begin{align}
    u(x,y) &= \E[\int_0^\infty Z_t(A) dt ] \\
           &= \int_0^\infty \E[Z_t] p_t(x,A) dt \\
        &= \int_0^\infty e^{-\alpha t} p_t(x,A) dt \\
        &= \int_0^\infty \P^x\{ \tau_\dagger < t \; \& \; B_t \in A \} dt \\
        &= \E[ \int_0^{\tau_\dagger} \one_A(B_t) dt ]  .
\end{align}
If we define
$\tau_A$ to be the hitting time of $A$ by $B$,
and $\mu(x,A)$ to be the hitting distribution of $\partial A$ by $B_{\min(t,\tau)}$,
by the strong Markov property this is equal to
\begin{align}
    u(x,y) &= \E^x[ \int_0^{\tau_\dagger} \one_A(B_t) dt ] \\
           &= \P^x\{ \tau_A < \tau_\dagger \}  \E^{\mu(x,A)}[ \int_0^{\tau_\dagger} \one_A(B_t) dt ] .
\end{align}
If $A$ is circular, the latter expectation will not depend on $x$;
call this $h(A)$.

Now consider the chance that $Z$ ever hits $A$.
If we make the approximation that $Z$ hits $A$ iff the trunk of $Z$ does,
then this is equal to
\begin{align}
    F(x,y) &= \int_0^\infty (1-p_e(t)) \P\{ \tau_A \in dt \} \\
           &= \int_0^\infty e^{\alpha t} (1-p_e(t)) e^{- \alpha t } \P\{ \tau_A < t \} dt \\
    &=\int_0^\infty e^{\alpha t} (1-p_e(t)) \P\{ \tau_A < t < \tau_\dagger \} dt \\
    &\approx \frac{1}{\E[K]} \int_0^\infty \P\{ \tau_A < t < \tau_\dagger \} dt \\
    &= \frac{1}{\E[K]} \int_0^\infty \P\{ \tau_A < t < \tau_\dagger \} dt \\
    &= \frac{1}{\E[K]} \P^x[ \tau_A < \tau_\dagger ] .
\end{align}
Therefore, we have that
\begin{align}
    F(x,y) \E[K] 
    \approx \P^x[ \tau_A < \tau_\dagger ] 
    = u(x,y) / h(A) .
\end{align}

Now, 
\begin{align}
    q(y)  &= \int_{\partial B(r_0)} \gamma(x) u(x,y) dx  \\
          &= h(A) \int_{\partial B(r_0)} \gamma(x) F(x,y) dx \\
          &= \frac{ h(A) }{ \E[K] } \migrate(y) .
\end{align}
The function $h(A)$ is the expected amount of time that a Brownian motion begun on the edge of a disk of area $A$
is expected to spend inside the disk before $\tau_\dagger$.
This is integral of the Green function for the Bessel process of the appropriate order, 
so using Borodin \& Salminen (Appendix 1),
and letting $w$ be the width of the patch,
in $d=1$,
\begin{align}
    h_1(A) % &= \E^w[ \int_0^\tau \one_A(B_t) dt ] 
  % &= \int_0^{2w} G_\alpha(0,y) dy \\
  &= \int_0^{2w} \frac{ e^{- y \sqrt{2\alpha} }}{\sqrt{2\alpha}} dy \\
  &= (1-e^{-2w\sqrt{2\alpha}})/(2\alpha)
\end{align}
and in $d=2$, by \citet{gradshteyn2007table} 5.56.2,
\begin{align}
    h_2(A) % &= \E^w[ \int_0^\tau \one_A(B_t) dt ] 
    % &= \int_0^{2w} G_\alpha(0,y) dy \\
  &= \int_0^{2w} 2 y K_0(y \sqrt{2\alpha}) dy \\
  &= \frac{1}{\alpha}\int_0^{2w\sqrt{2\alpha}} y K_0(y) dy \\
  &= \frac{1}{2\alpha}\left(1- 2w\sqrt{2\alpha} K_1(2w\sqrt{2\alpha}) \right)  .
\end{align}
